A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-02-27 analysis/paper/paper.Rmd
finally got the citations to work both in tables and in the paper

---
title: "A comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
bibliography: references.bib
csl: nature-biotechnology.csl
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
mainfont: Open Sans

@@

We created a transparent scoring scheme to check the quality of each method (`r ref("stable", "qc_checks")`), based on several existing tool quality and programming guidelines in literature and online. The goal of this quality control is in the first place to stimulate the improvement of current methods, and the development of user and developer friendly new methods. The quality control assessed 6 categories, each looking at several aspects, which are further divided into individual items. The availability category checks whether the method is easily available, whether the code and dependencies can be easily installed, and how the method can be used. The code quality assesses the quality of the code both from a user perspective (function naming, dummy proofing and availability of plotting functions) and a developer perspective (consistent style and code duplication). The code assurance category is frequently overlooked, and checks for code testing, continuous integration [@beaulieu-jones_reproducibility_2017] and an active support system. The documentation category checks the quality of the documentation, both externally (tutorials and function documentation) and internally (inline documentation). The behaviour category assesses the ease by which the method can be run, by looking for unexpected output files and messages, prior information and how easy the trajectory model can be extracted from the output. Finally, we also assessed the certain aspects of the study in which the method was proposed, such as publication in a peer-reviewed journal, the number of dataset on which the usefulness of the method was shown, and the scope of method evaluation in the paper.

@@

# Acknowledgements
# References

<div id="refs"></div>

>>>>

---
title: "A comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
bibliography: references.bib
csl: nature-biotechnology.csl
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \ExecuteBibliographyOptions{sorting=none,sortcites=true,autocite=superscript}
mainfont: Open Sans

@@

```{r}
qc_references <- readRDS(derived_file("checks.rds", "4-method_characterisation"))$references %>% 
  str_split("[, \n]+") %>% 
  unlist() %>% 
  unique() %>% 
  discard(is.na) %>%
  glue::collapse(., ";") %>%
  paste0("[", ., "]")
```

We created a transparent scoring scheme to check the quality of each method (`r ref("stable", "qc_checks")`), based on several existing tool quality and programming guidelines in literature and online `r qc_references` . The goal of this quality control is in the first place to stimulate the improvement of current methods, and the development of user and developer friendly new methods. The quality control assessed 6 categories, each looking at several aspects, which are further divided into individual items. The availability category checks whether the method is easily available, whether the code and dependencies can be easily installed, and how the method can be used. The code quality assesses the quality of the code both from a user perspective (function naming, dummy proofing and availability of plotting functions) and a developer perspective (consistent style and code duplication). The code assurance category is frequently overlooked, and checks for code testing, continuous integration [@beaulieu-jones_reproducibility_2017] and an active support system. The documentation category checks the quality of the documentation, both externally (tutorials and function documentation) and internally (inline documentation). The behaviour category assesses the ease by which the method can be run, by looking for unexpected output files and messages, prior information and how easy the trajectory model can be extracted from the output. Finally, we also assessed the certain aspects of the study in which the method was proposed, such as publication in a peer-reviewed journal, the number of dataset on which the usefulness of the method was shown, and the scope of method evaluation in the paper.

@@

# Acknowledgements
